, PhD, PE

### 2020-09-25 manuscript/submission/coverletter/coverletter.tex
New cover letter to editor

We would like to thank both reviewers for their thoughtful and helpful comments. We are delighted that they found our submission a “well-written paper that makes a useful contribution to the accessibility literature regarding quantifying accessibility” as well as “a nice added-value to the extensive literature on the subject.”

We feel we have addressed each comment raised by the reviewers, both major and minor. In particular, we re-executed our analysis using network distances in place of the Euclidean distances used in the original manuscript; the findings of this analysis were inconsequential, and our decision to retain the Euclidean specification is detailed in the attached response to reviewers.

We are grateful for the opportunity to submit this revised manuscript for further review and consideration in {\em Environment and Planning B: Urban Analytics and City Science}.

>>>>

Please find attached the second revision of our manuscript, \emph{Modeling the
impacts of park access on health outcomes: a utility-based accessibility
approach.}  We are pleased that one of the original referees appears wholly
satisfied by  our revisions. Though we are disappointed that the other original
referee could not provide comment, we are grateful to have received additional
comments from a third referee.

Many of the comments from this new referee were extraordinarily helpful to us as
we seek to clarify the specific contribution of our work, and to ensure that it
reaches the broadest possible audience. In particular, the recommendation to remove
cemeteries from consideration modestly strengthened our econometric findings.
At the same time, we feel that the new referee made some comments that we
exhaustively addressed in our previous response to Referee 1 (using Euclidean
distances, spatial resolution), or that contradict the recommendations of the
original referee that did not re-review the manuscript (including data on park use).

An attached document provides a more detailed response to each of the new
referee's comments. We reiterate our willingness to supply more explanatory detail
on our distance and spatial resolution investigations in a supplemental file at
your invitation.

Lastly, we are grateful for the opportunity to submit this revised manuscript for
further review and consideration in {\em Environment and Planning B: Urban
Analytics and City Science}.
